---
title: "Challenge-4"
author: "Tang Ching Xian"
date: "04 SEPT 2023"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## Questions
<br>

Load the "CommQuest2023.csv" dataset using the `read_csv()` command and assign it to a variable named "comm_data." 

```{r, eval=TRUE,echo=TRUE}
# Load Tidyverse
library(tidyverse)
# Read the CSV file and assign it to the variable "comm_data"
comm_data <- read.csv("CommQuest2023_Larger.csv")
comm_data_org <- read.csv("CommQuest2023_Larger.csv")
```
<br>


#### Question-1: Communication Chronicles

Using the select command, create a new dataframe containing only the "date," "channel," and "message" columns from the "comm_data" dataset.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Create a new dataframe with selected columns
new_df1<- comm_data%>% select(date,channel,message)
# Overview of new dataframe
glimpse(new_df1)
```
<br>

#### Question-2: Channel Selection

Use the filter command to create a new dataframe that includes messages sent through the "Twitter" channel on August 2nd.

**Solution:**

```{r, eval=FALSE,echo=TRUE}
# Create new dataframe with filtered data
new_df2 <- comm_data %>%filter(channel == "Twitter", date == "2023-08-02")%>%select(channel,date,message)
glimpse(new_df2)
```
<br>

#### Question-3: Chronological Order

Utilizing the arrange command, arrange the "comm_data" dataframe in ascending order based on the "date" column.

**Solution:**

```{r, eval=F,echo=TRUE}
#Arrange the dataframe in ascending order based on the "date" column
arranged_data <- comm_data %>%arrange(date)
print(arranged_data)
```
<br>

#### Question-4: Distinct Discovery

Apply the distinct command to find the unique senders in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
#Use distinct() to find unique senders
unique_senders <- comm_data %>%distinct(sender)%>%select(sender)
print(unique_senders)
```
<br>

#### Question-5: Sender Stats

Employ the count and group_by commands to generate a summary table that shows the count of messages sent by each sender in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Group by sender and count messages
summary_table <- comm_data %>%group_by(sender) %>%summarise(count = n())
print(summary_table)

#Another method just using count()
##summary_table2 <- comm_data %>%group_by(sender)%>%count(sender)
#Break down of each message and count
##summary_table2 <- comm_data %>%group_by(sender)%>%*count(message)*

```
<br>

#### Question-6: Channel Chatter Insights

Using the group_by and count commands, create a summary table that displays the count of messages sent through each communication channel in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Group by channel and count messages
summary_table2 <- comm_data %>%group_by(channel) %>%summarise(count = n())
print(summary_table2)

#Another method 
##summary_table2 <- comm_data %>%group_by(channel) %>%count(channel)
```
<br>

#### Question-7: Positive Pioneers

Utilize the filter, select, and arrange commands to identify the top three senders with the highest average positive sentiment scores. Display their usernames and corresponding sentiment averages.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Filter for positive sentiment scores
positive_data <- comm_data %>%
  filter(sentiment> 0)

# Group by sender and calculate the average sentiment score
sender_avg_sentiment <- positive_data %>%
  group_by(sender) %>%
  summarise(avg_sentiment=mean(sentiment))

# Arrange senders in descending order of average sentiment score
top_senders <- sender_avg_sentiment %>%
  arrange(desc(avg_sentiment))

# Select the top three senders
top_three_senders <- top_senders %>%
  slice(1:3)

# Display the top three senders and their corresponding sentiment averages
print(top_three_senders)
```
<br>

#### Question-8: Message Mood Over Time

With the group_by, summarise, and arrange commands, calculate the average sentiment score for each day in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Group by date and calculate the average sentiment score for each day
daily_avg_sentiment <- comm_data %>%
  group_by(date) %>%
  summarise(avg_sentiment = mean(sentiment))

# Arrange the results in ascending order of date
daily_avg_sentiment <- daily_avg_sentiment %>%
  arrange(date)

# Display the dataframe with daily average sentiment scores
print(daily_avg_sentiment)

#another method
##daily<-comm_data%>%group_by(date)%>%summarise(mean(sentiment))%>%arrange(date)
  
```
<br>

#### Question-9: Selective Sentiments

Use the filter and select commands to extract messages with a negative sentiment score (less than 0) and create a new dataframe.

**Solution:**

```{r, eval=FALSE,echo=TRUE}

# Filter for messages with negative sentiment scores
negative_sentiment_data <- comm_data %>%
  filter(sentiment< 0)

new_df3<-negative_sentiment_data
print.Date(new_df3)

#another method
##negative<-comm_data%>%select(message,sentiment)%>%filter(sentiment<0)
```
<br>

#### Question-10: Enhancing Engagement

Apply the mutate command to add a new column to the "comm_data" dataframe, representing a sentiment label: "Positive," "Neutral," or "Negative," based on the sentiment score.

**Solution:**

```{r, eval=F,echo=TRUE}
# Mutate to add a new column "sentiment_label" based on sentiment scores
comm_data<-comm_data %>% select(sentiment) %>% mutate(positive = as.logical(sentiment > 0), neutral = as.logical(sentiment == 0), negative = as.logical(sentiment < 0))
print(comm_data)


#comm_data %>% select(sentiment) %>% mutate(sentiment_label = ifelse(as.logical(sentiment > 0), "Positive", ifelse(as.logical(sentiment < 0), "Negative", "Neutral")))
#print(comm_data)
```
<br>

#### Question-11: Message Impact

Create a new dataframe using the mutate and arrange commands that calculates the product of the sentiment score and the length of each message. Arrange the results in descending order.

**Solution:**

```{r, eval=F,echo=TRUE}
#SHINY ERROR, INTRA ERROR, UNABLE TO RESOLVE

comm_data %>% mutate(a = sentiment*nchar(comm_data_org$message))%>%arrange(desc(a)) 
print(comm_data)

```
<br>

#### Question-12: Daily Message Challenge

Use the group_by, summarise, and arrange commands to find the day with the highest total number of characters sent across all messages in the "comm_data" dataframe.

**Solution:**

```{r, eval=FALSE,echo=TRUE}
# Group by date and calculate the total number of characters sent on each day
daily_char_count <- comm_data %>%
  group_by(date) %>%
  summarise(total_characters = sum(nchar(message)))

#note:sum(nchar(message) can be replaced by length(message)

# Arrange the results in descending order of total_characters
daily_char_count <- daily_char_count %>%
  arrange(desc(total_characters))

# Get the day with the highest total_characters
day_with_highest_chars <- daily_char_count$day[1]

# Optionally, you can print the day with the highest total_characters
print(day_with_highest_chars)
```
<br>

#### Question-13: Untidy data

Can you list at least two reasons why the dataset illustrated in slide 10 is non-tidy? How can it be made Tidy?

**Solution:** 
1)X is not a data, can be left as NA to be recognised
2)empty rows/observations
3)+/- is not recognised 
4) too many variables in a column