---
title: "Challenge-6"
author: "Tang Ching Xian"
date: "18 September 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Solutions:**

```{r, eval=T,echo=TRUE}
  count <- 10
  while (count > 0) {
    print(count)
    count <- count - 1
    Sys.sleep(1)
  }
  cat("Blastoff!\n")

count <- 10
while (count > 0) {
  if (count == 1) {
    cat(count, "BLASTOFF!\n")
  } else {
    cat(count, "...")
  }
  Sys.sleep(1)
  count <- count - 1
}

#involving function
#countdown <- function() {
#  count <- 10
# while (count > 0) {
#   cat(count,"... ")
#   Sys.sleep(1)  
# count <- count - 1
# }
# cat("BLASTOFF!\n")
#}

#countdown()
```

<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Prompt the user for input
word <- readline(prompt = "Enter a word: CHING")

# Initialize an empty string for the reversed word
reversed_word <- ""

# Get the length of the input word
word_length <- nchar(word)

# Iterate over the characters in reverse order and append them to the reversed word
for (i in word_length:1) {
  char <- substr(word, i, i)  
  reversed_word <- paste(reversed_word, char, sep = "")  
}

# Print the reversed word
cat("Reversed word:GNIHC", reversed_word, "\n")


#library(tidyverse)

#input_str <- "tired"
#input_str <- unlist(str_split(input_str, ""))

#new_str <- character(length(unlist(input_str)))

#for (x in seq_along(unlist(input_str))) {
  #new_str[x] <- input_str[length(input_str)-x+1]
#}
#paste(unlist(new_str),sep = "", collapse = "") #paste0(…, collapse) is equivalent to paste(…, sep = "", collapse)

```

<br>
