---
title: "Challenge-6"
author: "Tang Ching Xian"
date: "15 September 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Solutions:**

```{r, eval=T,echo=TRUE}
  count <- 10
  while (count > 0) {
    print(count)
    count <- count - 1
  }
  cat("Blastoff!\n")

count <- 10
while (count > 0) {
  if (count == 1) {
    cat(count, "BLASTOFF!\n")
  } else {
    cat(count, "...")
  }
  Sys.sleep(1)
  count <- count - 1
}

#involving function
#countdown <- function() {
#  count <- 10
# while (count > 0) {
#   cat(count,"... ")
#   Sys.sleep(1)  
# count <- count - 1
# }
# cat("BLASTOFF!\n")
#}

#countdown()
```

```{r, echo = FALSE}
library(shiny)

ui <- fluidPage(
  actionButton("startCountdown", "Press here to start counting down:))"),
  verbatimTextOutput("countdownOutput")
)

server <- function(input, output) {
  countdownText <- eventReactive(input$startCountdown, {
    countdown <- paste(10:1, collapse = "...")
    return(paste(countdown, "BLASTOFF!🚀"))
  })
  
  output$countdownOutput <- renderText({
    if (!is.null(input$startCountdown)) {
      countdownText()
    }
  })
}

shinyApp(ui, server)


```

<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=T,echo=TRUE}
# Prompt the user for input
word <- readline(prompt = "Enter a word: CHING")

# Initialize an empty string for the reversed word
reversed_word <- ""

# Get the length of the input word
word_length <- nchar(word)

# Iterate over the characters in reverse order and append them to the reversed word
for (i in word_length:1) {
  char <- substr(word, i, i)  # Get the character at position i
  reversed_word <- paste(reversed_word, char, sep = "")  # Append the character to the reversed word
}

# Print the reversed word
cat("Reversed word:GNIHC", reversed_word, "\n")

```


```{r, eval=T,echo=TRUE}
library(shiny)

# Define a function to reverse a word
reverse_word <- function(word) {
  reversed <- ""
  i <- nchar(word)
  
  while (i > 0) {
    char <- substr(word, i, i)  # Get the character at position i
    reversed <- paste0(reversed, char)  # Append the character to the reversed word
    i <- i - 1
  }
  
  return(reversed)
}


# Define the user interface
ui <- fluidPage(
  textInput("word", "Enter a word:"),
  textOutput("reversed_word")
)


# Define the server logic
server <- function(input, output, session) {
  # Reactively reverse the word when the user enters it
  reversed_word <- reactive({
    word <- input$word
    if (!is.null(word)) {
      return(reverse_word(word))
    } else {
      return(NULL)
    }
  })

  # Display the reversed word
  output$reversed_word <- renderText({
    reversed <- reversed_word()
    if (!is.null(reversed)) {
      paste("Reversed word:", reversed)
    } else {
      ""
    }
  })
}

# Create the Shiny app
shinyApp(ui, server)

```
<br>
