---
title: "NM2207 QUIZ"
author: "Tang Ching Xian"
date: "2023-09-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r,echo=TRUE,eval=TRUE}

# Load Tidyverse
library(tidyverse)
# Read the CSV file and assign it to the variable "titanic data"
titanic_data <- read.csv("titanic.csv")
# Overview of csv
glimpse(titanic_data)
survivors_class3 <- titanic_data %>%filter(Pclass == 3, Survived==1)

print(survivors_class3)

female_survivors_class3 <- survivors_class3%>%filter(Sex=="female")
number_of_female<-female_survivors_class3%>%summarise(count = n())
print(number_of_female)

avg_age_in_class3 <- survivors_class3 %>%
  summarise(mean_avg_age_in_class3 = mean(Age, na.rm = TRUE))
mean(mean_avg_age_in_class3$avg_age_in_class3)

avg1_age_in_class3 <- survivors_class3 %>%summarise(mean(survivors_class3$age))
mean(avg1_age_in_class3)


#survivors_class3_sorted <- survivors_class3[order(survivors_class3$Age, decreasing = TRUE), ]
#survivors_class3_sorted

survivors_class3_sorted <- survivors_class3 %>%
  arrange(desc(Age))
  
plot(survivors_class3$PassengerId, survivors_class3$Age, xlab = "Passenger ID", ylab = "Age", type = "b")
```




                                           
                                           
                                           
                                           
                                           
                                           
                                           
```{r,echo=TRUE,eval=TRUE}
                                       
# a. Filter the dataset to include only products in the Electronics category.
filtered_data <- product_info[product_info$Category == "Electronics", ]

# b. Calculate the average price of products in this category
average_price <- mean(filtered_data$Price)                                         
```                                             



Confusing...

Here's an example code that illustrates this issue:

```{r,echo=TRUE,eval=TRUE}
# Define a global variable
global_var <- 10

# Function that uses the global variable
multiply_by_global <- function(x) {
  global_var * x
}

# Function that modifies the global variable
modify_global <- function() {
  global_var <<- 20
}

# Call the functions
result1 <- multiply_by_global(5)
print(result1)  # Output: 50

modify_global()
result2 <- multiply_by_global(5)
print(result2)  # Output: 100

```

In this example, the `multiply_by_global()` function relies on the global variable `global_var` to perform its calculation. However, the `modify_global()` function modifies the value of `global_var', result in the value of `global_var` is changed between function calls. This can make the code difficult to debug and reason about, especially in larger programs where the global variable may be modified by multiple functions.



```{r,echo=TRUE,eval=TRUE}```{r,echo=TRUE,eval=TRUE}
Question:
  
#Write a function called guessNum for a guessing game where the players must guess the value of a number stored in a variable answer,
#a. In the first step, take the user's guess as the argument 
#b. In the local scope of guessNum, initialize the value of the variable answer to be 15
#c. Compare the user’s guess with the variable answer
#d. Print out an appropriate message to the console, telling them if guess was above, below, or right on the number stored in answer
#e. In the global scope, initialize the value of a variable guess to be 16. Write the function call for the guessNum function, using guess as the argument.

Ans:
# defining the guessNum function
guessNum <- function(guess) {
  # initializing the value of the variable answer
  answer <- 15
  
  # comparing the user's guess with the answer
  if (guess > answer) {
    message("Your guess is above the number.")
  } else if (guess < answer) {
    message("Your guess is below the number.")
  } else {
    message("Congratulations! Your guess is right on the number.")
  }
}

# initializing the value of the variable guess
guess <- 16

# calling the guessNum function with guess as the argument
guessNum(guess)                 
```


```{r,echo=TRUE,eval=TRUE}

Question:
#Evaluate the code in RStudio. Explain what the code below does and the reason for the output.

#multiply <- function(value){

#function_inside_function<-function(multiplier){

#return(multiplier*value)

#}

#return(function_inside_function(10))

#}

#function_inside_function(50)


The code defines a function called "multiply" that takes a single argument called "value".
Inside the "multiply" function, there is another function defined called "function_inside_function". This inner function takes a single argument called "multiplier".
The inner function returns the product of "multiplier" and "value".
Outside of the inner function, the "multiply" function returns the result of calling the inner function with the argument 10.
When the code is evaluated, it will return the value of 100, which is the result of calling the inner function with 10 as the "multiplier" argument.
When the code is evaluated, it will not output anything because the functions are defined but not executed.

If we were to execute the "multiply" function and pass it a value, for example, `multiply(5)`, it would return 50. This is because the nested function "function_inside_function" is called with an argument of 10, and it multiplies this parameter with the "value" parameter (5 in this case), resulting in 50.

However, when we try to call the nested function directly with "function_inside_function(50)", it will raise an error. This is because the nested function is only defined within the scope of the outer "multiply" function and cannot be accessed outside of it.
```


```{r,echo=TRUE,eval=TRUE}
For Loop:

    A for loop is used when you know in advance how many times you want to repeat a particular set of statements.
    It consists of an initialization step, a condition to check at each iteration, and an update step.
    The loop continues to execute as long as the condition is true.
    Once the condition becomes false, the loop terminates.

Here's a basic example in R of a for loop that prints numbers from 1 to 5:

R

for (i in 1:5) {
  print(i)
}

While Loop:

    A while loop is used when you want to repeat a set of statements as long as a specific condition is true.
    Unlike the for loop, a while loop does not require you to know in advance how many iterations are needed.
    It continues executing as long as the condition remains true, and when the condition becomes false, the loop stops.

Here's an example in R of a while loop that prints numbers from 1 to 5:

R

i <- 1
while (i <= 5) {
  print(i)
  i <- i + 1
}
```


